XXXXX

### 2014-09-29 paper/paper1.tex
revised R-200-NEGATIVE-LITERAL-CONSTRAINTS example

A matching triple has any literal except those excluded by the '-' operator.

\begin{ex}
<Jedi> {
    :feelingForce 'true'^^xsd:boolean ,
    :attitute 'good'^^xsd:string ,
    :laserSwordColor 'blue'^^xsd:string ,
    :numberLaserSwords '1'^^xsd:nonNegativeInteger }
<Sith> {
    :feelingForce 'true'^^xsd:boolean ,
    :attitute - 'good'^^xsd:string ,
    :laserSwordColor - 'blue'^^xsd:string ,
    :numberLaserSwords '2'^^xsd:nonNegativeInteger }
\end{ex}

@@

\begin{ex}
:Joda 
    :feelingForce 'true'^^xsd:boolean ;
    :attitute 'good'^^xsd:string ;
    :laserSwordColor 'blue'^^xsd:string ,
    :numberLaserSwords '1'^^xsd:nonNegativeInteger .
\end{ex}

@@

\begin{ex}
:DarthSidious
    :feelingForce 'true'^^xsd:boolean ;
    :attitute 'evil'^^xsd:string ;
    :laserSwordColor 'red'^^xsd:string ,
    :numberLaserSwords '2'^^xsd:nonNegativeInteger . 
\end{ex}

>>>>

A matching triple has any literal except those excluded by the '!' operator.

\begin{ex}
<Jedi> {
    :feelingForce (true) ,
    :attitute ('good') ,
    :laserSwordColor ('blue') ,
    :numberLaserSwords ('1'^^xsd:nonNegativeInteger) }
<Sith> {
    :feelingForce (true) ,
    :attitute (!'good') ,
    :laserSwordColor (!'blue') ,
    :numberLaserSwords ('2'^^xsd:nonNegativeInteger) }
\end{ex}

@@

\begin{ex}
:Joda 
    :feelingForce (true) ;
    :attitute ('good') ;
    :laserSwordColor ('blue') ,
    :numberLaserSwords '1'^^xsd:nonNegativeInteger .
\end{ex}

@@

\begin{ex}
:DarthSidious
    :feelingForce (true) ;
    :attitute ('evil') ;
    :laserSwordColor ('red') ,
    :numberLaserSwords '2'^^xsd:nonNegativeInteger . 
\end{ex}
